### 2025-09-21 simulation.qmd
20250911 - prevent R chunks in notes from running
20250921 - add package name to function

```{r}
load(url("https://osf.io/download/ues7n/"))
```
:::

@@

monteCarloSim_results <- SimDesign::runSimulation(
  design = Design,
  replications = 1000,
  generate = Generate,
  analyse = Analyse,
  summarise = Summarise,
  fixed_objects = list(proj_dists = proj_dists),
  seed = genSeeds(Design, iseed = 52242), # for reproducibility
  parallel = TRUE # for faster (parallel) processing
)
```

@@

>>>>

@@

load(url("https://osf.io/download/ues7n/"))
```
:::

monteCarloSim_results <- SimDesign::runSimulation(
  design = Design,
  replications = 1000,
  generate = Generate,
  analyse = Analyse,
  summarise = Summarise,
  fixed_objects = list(proj_dists = proj_dists),
  seed = SimDesign::genSeeds(Design, iseed = 52242), # for reproducibility
  parallel = TRUE # for faster (parallel) processing
)
```

@@

petersenlab::robust_load("https://osf.io/download/ues7n/") #load(url("https://osf.io/download/ues7n/"))
```
